### 2017-04-30 article/article.tex
Fixed bug

		\begin{align}
		\label{eq:x1_probability_yes}
			\begin{split}
				Pr(outlook = sunny, temperature = cool, humidity = normal, windy = false | play = yes) = \\
				Pr(play = yes) \cdot Pr(outlook = sunny | play = yes) \cdot Pr(temperature = hot 	| play = yes) \cdot \\
				Pr(humidity = normal 	| play = yes) \cdot Pr(windy = false 	| play = yes) = \\
				9/14 \cdot 2/9 \cdot 4/9 \cdot 6/9 \cdot 5/9 = 40/1701 = 0.02351557
			\end{split}
		\end{align}

		\begin{align}
		\label{eq:x1_probability_no}
			\begin{split}
			Pr(outlook = sunny, temperature = cool, humidity = normal, windy = false | play = no) = \\
			Pr(play = no) \cdot Pr(outlook = sunny | play = no) \cdot Pr(temperature = hot 	| play = no) \cdot \\
			Pr(humidity = normal 	| play = no) \cdot Pr(windy = false | play = no) =\\
			 5/14 \cdot 3/5 \cdot 1/5 \cdot 1/5 \cdot  2/5 = 3/875 = 0.003428571
		 \end{split}
		\end{align}

@@

		\begin{align}
		\label{eq:x2_probability_yes}
			\begin{split}
				Pr(outlook = overcast, temperature = mild, humidity = high, windy = true | play = yes) = \\
				Pr(play = yes) \cdot Pr(outlook = overcast | play = yes) \cdot Pr(temperature = mild | play = yes) \cdot \\
				Pr(humidity = high 	| play = yes) \cdot Pr(windy = true 	| play = yes) = \\
				9/14 \cdot 2/9 \cdot 4/9 \cdot 3/9 \cdot 4/9 = 16/1701 = 0.00940623
			\end{split}
		\end{align}

		\begin{align}
		\label{eq:x2_probability_no}
			\begin{split}
				Pr(outlook = overcast, temperature = cool, humidity = high, windy = true | play = no) = \\
				Pr(play = no) \cdot Pr(outlook = overcast | play = no) \cdot Pr(temperature = mild | play = no) \cdot \\
				Pr(humidity = high 	| play = no) \cdot Pr(windy = true | play = no) =\\
				5/14 \cdot 0/5 \cdot 2/5 \cdot 4/5 \cdot  4/5 = 0
			\end{split}
		\end{align}

>>>>

		\begin{align}
		\label{eq:x1_probability_yes}
			\begin{split}
				Pr(play = yes | outlook = sunny, temperature = cool, humidity = normal, windy = false) = \\
				Pr(play = yes) \cdot Pr(outlook = sunny | play = yes) \cdot Pr(temperature = hot 	| play = yes) \cdot \\
				Pr(humidity = normal 	| play = yes) \cdot Pr(windy = false 	| play = yes) = \\
				9/14 \cdot 2/9 \cdot 4/9 \cdot 6/9 \cdot 5/9 = 40/1701 = 0.02351557
			\end{split}
		\end{align}

		\begin{align}
		\label{eq:x1_probability_no}
			\begin{split}
			Pr(play = no | outlook = sunny, temperature = cool, humidity = normal, windy = false) = \\
			Pr(play = no) \cdot Pr(outlook = sunny | play = no) \cdot Pr(temperature = hot 	| play = no) \cdot \\
			Pr(humidity = normal 	| play = no) \cdot Pr(windy = false | play = no) =\\
			 5/14 \cdot 3/5 \cdot 1/5 \cdot 1/5 \cdot  2/5 = 3/875 = 0.003428571
		 \end{split}
		\end{align}

@@

		\begin{align}
		\label{eq:x2_probability_yes}
			\begin{split}
				Pr(play = yes | outlook = overcast, temperature = mild, humidity = high, windy = true) = \\
				Pr(play = yes) \cdot Pr(outlook = overcast | play = yes) \cdot Pr(temperature = mild | play = yes) \cdot \\
				Pr(humidity = high 	| play = yes) \cdot Pr(windy = true 	| play = yes) = \\
				9/14 \cdot 2/9 \cdot 4/9 \cdot 3/9 \cdot 4/9 = 16/1701 = 0.00940623
			\end{split}
		\end{align}

		\begin{align}
		\label{eq:x2_probability_no}
			\begin{split}
				Pr(play = no | outlook = overcast, temperature = cool, humidity = high, windy = true) = \\
				Pr(play = no) \cdot Pr(outlook = overcast | play = no) \cdot Pr(temperature = mild | play = no) \cdot \\
				Pr(humidity = high 	| play = no) \cdot Pr(windy = true | play = no) =\\
				5/14 \cdot 0/5 \cdot 2/5 \cdot 4/5 \cdot  4/5 = 0
			\end{split}
		\end{align}
